\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
minor changes to pseudocode

		\begin{algorithmic}[1]
			{\scriptsize
			\START[$\opn{init}_p$]{{\bf upon}}{$()$}
			\State $m_p\gets \emptyset$
			\State $\sigma_p\gets \bot$
			\END
			\START[$\opn{GC-propose}_p$]{{\bf upon}}{$(c)$}
			\State {\bf call} $\opn{announce}_p\left( c \right)$
			\END
			\Statex
			\START[$\opn{suggest}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $\opn{propose}_p( c,\mathcal{D})$ 			
			\END
			\Statex
			\START[$\opn{commit}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $m_p \gets m_p \oplus \left[ c \mapsto \mathcal{D}\right]$	
			\State $\sigma_p \gets  \opn{c-struct}\left(m_p\right)$
			\State $\opn{GC-decide}_p(\sigma_p)$		
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo3}
}
\subfigure[$\texttt{init}_p$ and $\texttt{announce}_p$ implementations.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			{\scriptsize
			\START[\texttt{init$_p$}]{{\bf upon}}{$()$} \label{alg:init}
			\State $cmds_p\gets\emptyset$ \label{alg:init-cmds}
			\State $\forall c,$ $deps_p[c]\gets \emptyset$ \label{alg:init-deps}
			\State $\forall c,$ $heard_p[c]\gets \emptyset$ \label{alg:init-heard}
			\State $\forall c,$ $suggested_p[c]\gets false$ \label{alg:init-suggested}
			\END
			\Statex
			\START[\texttt{announce$_p$}]{{\bf upon}}{$(c)$} \label{alg:announce}
			\State $cmds_p\gets cmds_p\cup\{c\}$ \label{alg:add-command}
			\State $\forall q\in P$ {\bf send} $\langle \texttt{cmd}$ $|$ $c \rangle$ {\bf to} $q$\label{alg:send-new-cmd}
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo1}
}	
\hspace*{0.1in}\subfigure[receive of \texttt{cmd} and \texttt{deps} messages, and suggestion of dependencies for a command on process $p$.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			\makeatletter
			\setcounter{ALG@line}{8}
			\makeatother
			{\scriptsize
			\START[$\langle \texttt{cmd}$ $|$ $c \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-new-cmd}
			\State $\mathcal{D} \gets \{ d : d \in cmds_p \land$\label{alg:update-d}
			\Statex \hspace{2cm}$\land d\neq c \land d \asymp c \}$
			\State $cmds_p\gets cmds_p\cup\{c\}$\label{alg:update-cmds-p}
			\State {\bf send} $\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$ {\bf to} $q$\label{alg:send-deps}
			\END
			\Statex
			\START[$\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-deps}
			\State $deps_p[c]\gets deps_p[c]\cup \mathcal{D}$\label{alg:update-deps-p}
			\State $heard_p[c]\gets heard_p[c]\cup \{q\}$
			\END
			\Statex
			\START[]{{\bf upon}}{$\exists c$ $:$ $ | heard_p[c] | \geq \mathcal{Q}$ $\land$} \label{alg:receive-deps}
			\Statex \hspace{1cm}$\land$ $suggested_p[c]=false$
			\State $suggested_p[c]\gets true$
			\State {\bf call} $\texttt{suggest}_p(c,deps_p[c])$ \label{alg:call-suggest}
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo2}
}
\caption{Example of dependency-set algorithm and leaderless generalized consensus implementations.}
\label{fig:deps-set-algo}
\end{figure*}

>>>>

		\begin{algorithmic}[1]
			{\scriptsize
			\START[$\opn{init}_p$]{{\bf upon}}{$()$}
			\State $m_p\gets \emptyset$
			\State $\sigma_p\gets \bot$
			\END
			\START[$\opn{GC-propose}_p$]{{\bf upon}}{$(c)$}
			\State {\bf call} $\opn{announce}_p\left( c \right)$
			\END
			\Statex
			\START[$\opn{suggest}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $\opn{propose}_p( c,\mathcal{D})$ 			
			\END
			\Statex
			\START[$\opn{commit}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $m_p \gets m_p \oplus \left[ c \mapsto \mathcal{D}\right]$	
			\State $\sigma_p \gets  \opn{c-struct}\left(m_p\right)$
			\State $\opn{GC-decide}_p(\sigma_p)$		
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo3}
}
\hspace*{0.1in}\subfigure[Example of dependency-set algorithm implementation - part 1.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			{\scriptsize
			\START[\texttt{init$_p$}]{{\bf upon}}{$()$} \label{alg:init}
			\State $cmds_p\gets\emptyset$ \label{alg:init-cmds}
			\State $\forall c,$ $deps_p[c]\gets \emptyset$ \label{alg:init-deps}
			\State $\forall c,$ $heard_p[c]\gets \emptyset$ \label{alg:init-heard}
			\State $\forall c,$ $suggested_p[c]\gets false$ \label{alg:init-suggested}
			\END
			\Statex
			\START[\texttt{announce$_p$}]{{\bf upon}}{$(c)$} \label{alg:announce}
			\State $cmds_p\gets cmds_p\cup\{c\}$ \label{alg:add-command}
			\State $\forall q\in P$ {\bf send} $\langle \texttt{cmd}$ $|$ $c \rangle$ {\bf to} $q$\label{alg:send-new-cmd}
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo1}
}	
\hspace*{0.1in}\subfigure[Example of dependency-set algorithm implementation - part 2.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			\makeatletter
			\setcounter{ALG@line}{8}
			\makeatother
			{\scriptsize
			\START[$\langle \texttt{cmd}$ $|$ $c \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-new-cmd}
			\State $\mathcal{D} \gets \{ d : d \in cmds_p \land$\label{alg:update-d}
			\Statex \hspace{2cm}$\land d\neq c \land d \asymp c \}$
			\State $cmds_p\gets cmds_p\cup\{c\}$\label{alg:update-cmds-p}
			\State {\bf send} $\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$ {\bf to} $q$\label{alg:send-deps}
			\END
			\Statex
			\START[$\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-deps}
			\State $deps_p[c]\gets deps_p[c]\cup \mathcal{D}$\label{alg:update-deps-p}
			\State $heard_p[c]\gets heard_p[c]\cup \{q\}$
			\END
			\Statex
			\START[]{{\bf upon}}{$\exists c$ $:$ $ | heard_p[c] | \geq \mathcal{Q}$ $\land$} \label{alg:receive-deps}
			\Statex \hspace{1cm}$\land$ $suggested_p[c]=false$
			\State $suggested_p[c]\gets true$
			\State {\bf call} $\texttt{suggest}_p(c,deps_p[c])$ \label{alg:call-suggest}
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo2}
}
\caption{Leaderless generalized consensus, and example of dependency-set algorithm implementation.}
\label{fig:deps-set-algo}
\end{figure*}
